Something fancy...

### 2020-02-28 draft.tex
.

For symmetry-protected topological systems in one dimension there is a well-known relation between ES and the Zak phase \carlos{cite}. The Zak phase, which is quantized, is zero whenever there is an even number per edge of eigenvalues at $\xi = 1/2$, and $\pi$ when the number is odd. Beyond symmetry protected systems, there was observed that in the fully dimerized SSH chain, with only a single mode present in the ES, the Zak phase is equal to the midgap eigenvalue \cite{Ryu2006}. For cases with more edge modes present in the ES it has been shown that the Zak phase follows the midgap eigenvalues qualitatively \cite{Huang2012,Huang2012-2}. The first result we show is that in systems with nearest-neighbor hopping, like the SSH chain, one can obtain the Zak phase by ordering the eigenvalues of the ES, $\xi_1 < \xi_2 < ...$, and computing
\begin{equation}
\chi = \frac{1}{2}\left(\sum_j (-1)^j \xi_j+N_A\right) \, {\rm mod} \, 1,
\label{eqplusminus}
\end{equation}
where $N_A$ is the number of electrons in the ground state in region A, which in the thermodynamic limit fulfills
\begin{equation}
\lim_{L \rightarrow \infty} \gamma = \lim_{L \rightarrow \infty} \chi.
\end{equation}
\carlos{Note: Peschel only finds the entanglement energies to be equispaced in systems with nearest-neighbor hopping. The general picture is seems much more complex. So far it worked for the two-band models I considered because they effectively only have nearest-neighbor hopping, adding a $\sigma_0$ hopping for example breaks this. See in Fig.\ref{eh} that for $t'\neq 0$ this is not true anymore, and even in the $\nu=1$ phase there can be crossings.  }

\begin{figure}[h!]
\centering
\includegraphics[width=80mm]{eh1.pdf}
\caption{Entanglement energy spectrum for a cut with $t'=-2$.}
\label{eh}
\end{figure}

@@

\subsubsection{Multiple edge modes}
%\subsubsection{Localization dependent charges}
\carlos{change title.}
In expression 	\eqref{eqplusminus} we assigned a charge of $\pm1/2$ to each entanglement eigenstate depending on the eigenvalue ordering. 
In order to generalize this to systems with longer-range hopping one needs to know how to properly assign this $\pm 1/2$ charge to each entanglement mode. We found that this is done according to their localization, so we have
\begin{equation}
\chi = \frac{1}{2} \left( \sum_{i\in r}\xi_i-\sum_{i\in l}\xi_i \pm \sum_{i\in b}\xi_i  + N_A \right) \quad {\rm mod} \quad 1,
\label{loceq}
\end{equation}
by defining $ \chi$ modulo $1$ we make the charge of the bulk modes irrelevant but in the next section we will have to take a closer look at it. We find the charge of the edge modes by computing $\expval{\hat{X}}_i$ and seeing if it is above or below $L/4$. In the case the ES is double degenerate at most, left and right edge states might mix but one will always classify one state of the pair as left and the other one as right, this is however not the case when the degeneracies are higher than two-fold. In order to ensure that we obtain edge modes localized at one edge, instead of $C_A$ we diagonalize $C_A + \lambda C_A\hat{X}C_A$, where $\hat{X}$ is the position operator and $\lambda$ is a small parameter that vanishes in the thermodynamic limit.

The reason expression~\eqref{loceq} simplifies so much for systems with nearest-neighbor hopping is that in this case it was found that all the eigenvalues of the ES are related to each other. The entanglement energies  (\carlos{Peschel always refers to them as entanglement energies or eigenvalues of the entanglement Hamiltonian. Entanglement spectrum he uses for the spectrum of the reduced density matrix, so it makes sense to use single-particle ES for the spectrum of CA}) come in pairs of left and right modes that are equispaced in the thermodynamic limit, so that the charges assigned are always $ \pm(+-+-+-...)$. In the case that the modes cross each other they do so for every pair, so that it just ammounts to a global minus sign in the charge assignment.

This relation between the Zak phase and the entanglement spectrum is a consequence of an identity between the Zak phase and the many-body entanglement spectrum previously found for infinite chains \cite{Zaletel2014}. In Appendix A (\carlos{I have to take a look at it again}) we modified this derivation to account for the periodic boundary conditions we use and show how their result reduces to Eq.~\eqref{loceq} when expressing it in terms of the ES.

@@

In reference \cite{Zaletel2014} translational invariance was used to derive Eq. \ref{zaletel} in Appendix A. Say we break translational invariance by adding weak disorder to the system. This will modify slightly the entanglement spectrum but not the charge assignment. Without translational invariance the entanglement spectrum will depend on where is the cut placed on the ring, even though the ground state, and therefore the Zak phase, will not. The first quantity one can construct that is cut-independent is the cut-average of $\chi$. Naively one would define
\begin{equation}
\bar{\chi} = \frac{1}{L}\sum_{s=1}^L \chi_s
\label{batcutavg}
\end{equation}
where
\begin{equation}
\chi_s = \frac{1}{2} \left( \sum_{i\in r}\xi^s_i-\sum_{i\in l}\xi^s_i \pm \sum_{i\in b}\xi^s_i  + N_A \right) \quad {\rm mod} \quad 1,
\end{equation}
is defined for cuts at $s$ and $s+L/2$. However the average of a circular quantity is not well defined. The reason we took the modulo 1 was to get rid of the bulk contribution, which should vanish in the end result anyway. If we take the modulo 1 after averaging we still might have an issue due to the bulk classification being inconsistent. A bulk mode near the center of A, at $L/4$, might cross $L/4$ at different cuts, changing its assigned charge. The bulk contribution will not be constant across cuts and that will lead to errors when averaging.

One can get away with expression Eq.~\eqref{batcutavg} in a few cases. For a system with a continuous position-dependent Hamiltonian in a trivial phase, $\chi_s$ should also be continuous. This tell us how we have to perform the cut-average. Even when discontinuities are present as long they are weak enough so that we still can tell when $\chi_s$ crosses $0,1$, we can use this information to perform the cut average. In the case that the width of $\chi_s$ is lower than 1 one can select the range of values so that $\chi_s$ does not cross the "$0,1$" line and then average. We show this in Fig.\ref{inh}.a for a system with disorder on $\kappa_s$. Note that even though we have random disorder the ES, and therefore $\chi_s$ shows some sign of continuity so that the cut-averaged can be performed this way even for relatively strong disorder.

@@

\makebox[0pt]{
\subfloat[$\kappa_s$]{
  \includegraphics[width=40mm]{4_a.pdf}
}
\subfloat[$t=1,t'=2,m =1$]{
  \includegraphics[width=40mm]{4_b.pdf}
}
}
\label{inh}
\end{figure}

In the case where $\chi_s$ is continuous but the width is larger than 1 can construct a new quantity $\chi_s'$ that is not defined modulo 1, by extending the range of $\chi_s \, {\rm mod} \, 1$ every time it crosses $0$ or $1$, such that
\begin{equation}
\chi_{s+1}' = {\rm Min}\{\chi'_{s+1}-\chi'_s,\chi'_{s+1}-\chi'_s+1,\chi'_{s+1}-\chi'_s-1\}
\end{equation}
where at each step $\chi_{s+1}'$ is chosen by minimizing the absolute value of the difference. In Fig.\ref{inh}.b we show an example of this. In Fig.\ref{disorder} we show $1-\expval{\chi_s}_{\rm cuts}/\gamma$ for different system lengths for system with weak disorder, as well as the disorder average of $1-\chi_0/\gamma$. We observe that both averages lead to the same difference, which scales as $O(L^{-2})$ (\carlos{I have to redo de plot, maybe scaling is different}), vanishing in the thermodynamic limit. The fact that both methods lead to the same error suggests that it comes strictly from a systematic finite size error in the computation of either the Zak phase or the ES which is system-independent.

@@

In a general case where the discontinuities are too strong and the discussed above does not apply one has to take a closer look into the bulk states to ensure a consistent classification. As we mentioned above the bulk states farthest away from the edges are the problematic ones. They are also the ones best approximated by the Wannier states obtained from the chain with periodic boundary conditions as the eigenstates of 
\begin{equation}
C\hat{X}_{\rm PBC}C
\end{equation}
where $\hat{X}_{\rm PBC} = \exp\{i 2\pi \hat{X}/L\}$. Similar to when we go through different cuts labeled by $s$, we now consider the Wannier states dependent on where we define our lattice site 1, shifted by $s$. The obtained Wannier states for $s$ and $s+1$ will be therefore exctly the same, but shifted one lattice site. By considering their average position $\expval{\hat{X}_{PBC}}_{i,s}$ we can define a set of $2L$ Wannier states that depend continuously on $s$ (provided that the Hamiltonian is continuous). These Wannier states are then a good approximation for the Bulk states of $C_A$ we find for the different cuts. Consider now the quantity $\sum_i\expval{\hat{X}}_{i,s}$. So far everything was $s$ independent as our system was periodic, but by considering the operator $\hat{X}$ we introduce an unphysical boundary so that it will depend on where we put the first and last sites. If the states do not cross this unphysical boundary then $\sum_i\expval{\hat{X}}_{i,s} = \sum_i\expval{\hat{X}_{\rm PBC}}_{i,s} $ and it will be a constant. However, when a Wannier state crosses the boundary we obtain the same constant plus $L$. If we put this boundary at $L/4$ the object 
\begin{equation}
\frac{1}{L}\left(\sum_i\expval{\hat{X}}_{i,s}-\sum_i\expval{\hat{X}}_{i,0}\right)
\end{equation}
will be 1 (0) when a states has crossed the boundary or 0 (-1) when it has not, depending on the number of states in A at $s=0$, which we take as reference. Depending which state we take as reference will introduce a global integer shift for all cuts, so it is not relevant as it will go away after we average and take the modulo 1. By adding this term to our cut-average we will compensate for when our bulk state in the middle of A crosses $L/4$ and its charge changes. Leading to a continuous $\chi_s$ which can be averaged. In Fig.\ref{wan} we show how this works for one case. In Fig.\ref{wan}.a we show the expectation value of the position operator for both the entanglement eigenstates (in black) and the Wannier states (in red) for different cuts. In Fig.\ref{wan}.b and c we show $\chi_s$, which displays jumps due to a bulk state crossing $L/4$, and 
\begin{equation}
\chi_s' = \chi_s + \frac{1}{L}\left(\sum_i\expval{\hat{X}}_{i,s}-\sum_i\expval{\hat{X}}_{i,0}\right),
\end{equation}
where the position is defined in $[-3L/4,L/4]$ to correctly compensate for these jumps. This method conceptually works perfectly whenever the bulk states of the ES match the Wannier states, i.e. in the thermodynamic limit, but it is not clear what the small parameter is. It depends on the $\lambda$ used (it should be small enough to not affect ES but large enough to localize the ES eigenstates) but also on the model. Models with longe-range hopping, for example, lead to a higher number of edge modes in the ES which makes the effect of the edge go deeper into the bulk. 
\carlos{We should think again if there is a better method to get this}

\begin{figure}[h!]
\centering
\makebox[0pt]{
\subfloat[$\expval{\hat{X}}_{i,s}$ for different cuts, for the entanglement eigenstates (black) and the Wannier states (red)]{
  \includegraphics[width=90mm]{loca.pdf}
}}\hspace{0mm}

@@

\caption{a)Profile used for the inhomogeneous part $\kappa_s$. b,c,d) ES (black), $\chi_s$ mod $1$ (green), $\gamma$ (red), $\expval{\chi_s}_{\rm cuts}$ mod $1$ (dashed blue).}
\label{wan}
\end{figure}

@@

The proof in Ref.\cite{Zaletel2014} also breaks down for superconducting systems. However, as we did for systems without translational invariance, one can extend expression \ref{mainl} for systems with pairing terms as well. Since one computes the Zak phase from the single-particle Bogoliubov-de Gennes Hamiltonian, we can obtain the correspondent entanglement spectrum and use expression \ref{mainl} to obtain the Zak phase. Take for example the kitaev chain, with the following Hamiltonian
\begin{align*}
H =& -\mu \sum_{i} c_i^\dagger c_i - t \sum_{i}\left( c_{i+1}^\dagger c_i + {\rm h.c.}\right) \\
&+  \sum_{i}\left( \Delta c_{i} c_{i+1} + {\rm h.c.}\right).
\end{align*}
Using the spinor $\phi_i^\dagger = (c_i^\dagger, c_i)$, we can rewrite the Hamiltonian as
\begin{align*}
&H = \frac{1}{2}\sum_i \phi^\dagger_i H_{BdG,ij} \phi_j,\\
&H_{BdG,ij} = -\mu \tau_z \delta_{ij} - (t \tau_z + i\Delta \tau_y )\delta_{i,j+1}- (t \tau_z - i\Delta \tau_y)\delta_{i,j-1}.
\end{align*}
Note that by taking $t' = \kappa = \kappa = 0$ in the BDI model, Eq. \ref{bdi_model}, we obtain
\begin{align*}
H_{ij} =& m \sigma_x\delta_{ij} + \frac{1}{2} t \left[(\sigma_x + i \sigma_y)\delta_{i,j+1} + (\sigma_x - i \sigma_y) \delta_{i,j-1} \right],
\end{align*}
which is just the Bogoliubov-de Gennes Hamiltonian of the Kitaev chain by rotating $x$ into $z$ and identifying $\mu = -m, t_{\rm Kit} = -t_{BDI}/2, \Delta = -t_{BDI}/2 $. From Fig.\ref{bdi_phase_diagram} we see that the $BDI$ model transitions from $\nu = 1$ to the trivial phase at $t=0, m=\pm t_{BDI}$, or alternatively, when $\mu = \pm 2 t_{Kit}$, which is the known result for the Kitaev chain. Therefore the results already shown for the BDI model studied here are also applicable to the Kitaev chain.  
\carlos{check again becase I though that the kitaev chain had left-left right-right pairs, so in this case the entnsglement energies are not equispaced}

>>>>

For symmetry-protected topological systems in one dimension there is a well-known relation between ES and the Zak phase \cite{Peschel2008}. The Zak phase, which is quantized, is zero whenever there is an even number per edge of eigenvalues at $\xi = 1/2$, and $\pi$ when the number is odd. Beyond symmetry protected systems, there was observed that in the fully dimerized SSH chain, with only a single mode present in the ES, the Zak phase is equal to the midgap eigenvalue \cite{Ryu2006}. For cases with more edge modes present in the ES it has been shown that the Zak phase follows the midgap eigenvalues qualitatively \cite{Huang2012,Huang2012-2}. The first result we show is that in systems with nearest-neighbor hopping, like the SSH chain, one can obtain the Zak phase by ordering the eigenvalues of the ES, $\xi_1 < \xi_2 < ...$, and computing
\begin{equation}
\chi = \frac{1}{2}\left(\sum_j (-1)^j \xi_j+N_A\right) \, {\rm mod} \, 1,
\label{eqplusminus}
\end{equation}
where $N_A$ is the number of electrons in the ground state in region A, which in the thermodynamic limit fulfills
\begin{equation}
\lim_{L \rightarrow \infty} \gamma = \lim_{L \rightarrow \infty} \chi.
\end{equation}

@@

\subsubsection{General case}

In expression 	\eqref{eqplusminus} we assigned a charge of $\pm1/2$ to each entanglement eigenstate depending on the eigenvalue ordering. 
In order to generalize this to systems with longer-range hopping one needs to know how to properly assign this $\pm 1/2$ charge to each entanglement mode. We found that this is done according to their localization, so we have
\begin{equation}
\chi = \frac{1}{2} \left( \sum_{i\in r}\xi_i-\sum_{i\in l}\xi_i \pm \sum_{i\in b}\xi_i  + N_A \right) \quad {\rm mod} \quad 1,
\label{loceq}
\end{equation}
by defining $ \chi$ modulo $1$ we make the charge of the bulk modes irrelevant but in the next section we will have to take a closer look at it. We find the charge of the edge modes by computing $\expval{\hat{X}}_i$ and seeing if it is above or below $L/4$. In the case the ES is double degenerate at most, left and right edge states might mix but one will always classify one state of the pair as left and the other one as right, this is however not the case when the degeneracies are higher than two-fold. In order to ensure that we obtain edge modes localized at one edge, instead of $C_A$ we diagonalize $C_A + \lambda C_A\hat{X}C_A$, where $\hat{X}$ is the position operator and $\lambda$ is a small parameter that vanishes in the thermodynamic limit.

The reason expression~\eqref{loceq} simplifies so much for systems with only nearest-neighbor hopping is that it is known that in this case the eigenstates of $C_A$ always come with an alternating edge localization (left-right-left...), so that the signs assigned are always $ \pm(+-+-+-...)$. Their eigenvalues are also related, so that the modes can only cross each other if all of them do so two by two, so that it just ammounts to a global minus sign.

This relation between the Zak phase and the entanglement spectrum is a consequence of an identity between the Zak phase and the many-body entanglement spectrum previously found for infinite chains \cite{Zaletel2014}. In Appendix A we modified this derivation to account for the periodic boundary conditions we use and show how their result reduces to Eq.~\eqref{loceq} when expressing it in terms of the ES.

@@

In reference \cite{Zaletel2014} translational invariance was used to derive the relation between the many-body entanglement spectrum and the Zak phase. If this symmetry is broken by, for example, adding weak disorder to the system, this will modify slightly the eigenvalues of the reduced density matrix but not the charge assignment in Eq.~\eqref{zaletel} in the Appendix. The left side of Eq.~\eqref{zaletel} will be cut independent while the right side is not, and therefore cannot be correct.

We are interested therefore in finding a cut-independent quantity from the ES that might still result in the Zak phase. The first thing one can do is a cut-average of $\chi$. Naively one would define
\begin{equation}
\bar{\chi} = \frac{1}{L}\sum_{s=1}^L (\chi_s \, {\rm mod} \, 1 )
\label{batcutavg}
\end{equation}
where
\begin{equation}
\chi_s = \frac{1}{2} \left( \sum_{i\in r}\xi^s_i-\sum_{i\in l}\xi^s_i \pm \sum_{i\in b}\xi^s_i  + N_A \right) 
\end{equation}
is obtained for cuts at $s$ and $s+L/2$. However the average of a circular quantity is not well defined. The reason we defined $\chi$ with modulo 1 in Eq.~\eqref{loceq} was to get rid of the choice of sign for the bulk, which should not matter for the end result anyway. Instead, we can calculate
\begin{equation}
\bar{\chi} = \frac{1}{L}\sum_{s=1}^L \chi_s \quad {\rm mod} \quad 1 
\label{goodcutavg}
\end{equation}
but in order to obtain the correct result we need the contribution from the bulk to be constant across different cuts,$\xi_{i \in b}^s = \xi_{i \in b}$, so that in the end
\begin{align}
\bar{\chi} =& \frac{1}{2L}\sum_{s=1}^L \left( \sum_{i\in r}\xi^s_i-\sum_{i\in l}\xi^s_i \right) \quad {\rm mod} \quad 1 \\
&+\frac{1}{2} \left(\sum_{i\in b}\xi^s_i + N_A \right) \quad {\rm mod} \quad 1 \nonumber
\label{goodcutavg}
\end{align}
If instead we only take the modulo 1 after averaging we still might have an issue due to the charge assignment of the bulk modes being inconsistent. A bulk mode near the center of A, at $L/4$, might cross $L/4$ at different cuts, changing its assigned charge. The bulk contribution will not be constant across cuts and that will lead to errors when averaging.

One can get away with expression Eq.~\eqref{batcutavg} in a few cases. For a system with a continuous position-dependent Hamiltonian $\chi_s$ should also be continuous. This tell us how we have to perform the cut-average. Even when discontinuities are present as long they are weak enough so that we still can tell when $\chi_s$ crosses "$0,1$" (\carlos{write properly}), the cut-average can be performed. In the case that the width of $\chi_s$ is lower than 1 one can select the range of values so that $\chi_s$ does not cross the "$0,1$" line and then average. We show this in Fig.\ref{inh} for a system with disorder on $\kappa_s$. Note that even though we have random disorder, the ES and $\chi_s$ show some sign of continuity so that the cut-averaged can be performed this way even for relatively strong disorder.

@@

\makebox[0pt]{
\subfloat[$\kappa_s$]{
  \includegraphics[width=40mm]{4_a.pdf}
}
\subfloat[$t=1,t'=2,m =1$]{
  \includegraphics[width=40mm]{4_b.pdf}
}
}\hspace{0mm}

\makebox[0pt]{
\subfloat[$\chi_s'$]{
  \includegraphics[width=40mm]{xicfix.pdf}
}}
\label{inh}
\end{figure}

In the case where $\chi_s$ is continuous but the width is larger than 1 can construct a new quantity $\chi_s'$ that is not defined modulo 1, by extending the range of $\chi_s \, {\rm mod} \, 1$ every time it crosses $0$ or $1$. In Fig.\ref{inh}.d we show an example of this. In Fig.\ref{disorder} we show $1-\expval{\chi_s}_{\rm cuts}/\gamma$ for different system lengths for system with weak disorder, as well as the disorder average of $1-\chi_0/\gamma$. We observe that both averages lead to the same difference, which scales as $O(L^{-2})$ (\carlos{I have to redo de plot, maybe scaling is different}), vanishing in the thermodynamic limit. The fact that both methods lead to the same error suggests that it comes strictly from a systematic finite size error in the computation of either the Zak phase or the ES which is system-independent.

@@

\begin{figure}[t]
\centering
\makebox[0pt]{
\subfloat[$\expval{\hat{X}}_{i,s}$ for different cuts, for the entanglement eigenstates (black) and the Wannier states (red)]{
  \includegraphics[width=90mm]{loca.pdf}
}}\hspace{0mm}

@@

\caption{}
\label{wan}
\end{figure}

In a general case where the discontinuities are too strong and the discussed above does not apply one has to take a closer look into the bulk states to ensure a consistent charge assignment. As we mentioned above the bulk states farthest away from the edges are the problematic ones. They are also the ones best approximated by the Wannier states obtained from the chain with periodic boundary conditions, as the eigenstates of 
\begin{equation}
C\hat{X}_{\rm PBC}C
\end{equation}
where $\hat{X}_{\rm PBC} = \exp\{i 2\pi \hat{X}/L\}$. Similar to when we go through different cuts labeled by $s$, we now consider the Wannier states dependent on where we define our lattice site 1, shifted by $s$. The obtained Wannier states for $s$ and $s+1$ will be therefore exactly the same, but shifted one lattice site. By considering their average position $\expval{\hat{X}_{PBC}}_{i,s}$ we can define a set of $2L$ Wannier states that depend continuously on $s$, provided that the Hamiltonian is continuous. These Wannier states are then a good approximation for the Bulk states of $C_A$ we find for the different cuts. 
Consider now the quantity $\sum_i\expval{\hat{X}}_{i,s}$. So far everything was $s$ independent as our system was periodic, but by considering the operator $\hat{X}$ we introduce an unphysical boundary so that it will depend on where we put the first and last sites. If the states do not cross this unphysical boundary then $\sum_i\expval{\hat{X}}_{i,s} = \sum_i\expval{\hat{X}_{\rm PBC}}_{i,s} $ and it will be a constant with $s$. However, when a Wannier state crosses the boundary we obtain the same constant plus $L$. If we put this boundary at $L/4$ the quantity 
\begin{equation}
\frac{1}{L}\left(\sum_i\expval{\hat{X}}_{i,s}-\sum_i\expval{\hat{X}}_{i,0}\right)
\end{equation}
will be 1 (0) when a states has crossed the boundary or 0 (-1) when it has not, depending on the number of states in A at $s=0$, which we take as reference. Depending which state we take as reference will introduce a global integer shift for all cuts, so it is not relevant as it will go away after we average and take the modulo 1. By adding this term to our cut-average we will compensate for when our bulk state in the middle of A crosses $L/4$ and its charge changes, leading to a continuous $\chi_s$ which can be averaged. In Fig.\ref{wan} we show how this works for one case. In Fig.\ref{wan}.a we show the expectation value of the position operator for both the entanglement eigenstates (in black) and the Wannier states (in red) for different cuts. In Fig.\ref{wan}.b and c we show $\chi_s$, which displays jumps due to a bulk state crossing $L/4$, and 
\begin{equation}
\chi_s' = \chi_s + \frac{1}{L}\left(\sum_i\expval{\hat{X}}_{i,s}-\sum_i\expval{\hat{X}}_{i,0}\right),
\end{equation}
where the position is defined in $[-3L/4,L/4]$ to correctly compensate for these jumps. This method conceptually works perfectly whenever the bulk states of the ES match the Wannier states, i.e. in the thermodynamic limit, but it is not clear what the small parameter is. It depends on the $\lambda$ used (it should be small enough to not affect ES but large enough to localize the ES eigenstates) but also on the system. Systems with many ES edge modes close to the bulk tend to have a higher finite size effect.

This method is however not general. We find that whenever there is an interphase in our system, and therefore a zero mode in the energy spectrum, the Wannier states are in general no longer a good approximation of the bulk of finite systems. However, in the cases where we have an interphase but $\chi_s$ is continuous and its width is lower than one, we observe that Eq.\eqref{batcutavg} still gives the correct Zak phase, suggesting that this relation between the ES and the Zak phase exists in general for inhomogeneous systems even though we do not know how to compute it in some cases.

@@

The proof in Ref.\cite{Zaletel2014} also breaks down for superconducting systems. However, as we did for systems without translational invariance, one can extend this identity for systems with pairing terms as well. Since one computes the Zak phase from the single-particle Bogoliubov-de Gennes Hamiltonian, we can obtain the correspondent ES and everything discussed above should apply as well. Take for example the kitaev chain, with the following Hamiltonian
\begin{align*}
H =& -\mu \sum_{i} c_i^\dagger c_i - t \sum_{i}\left( c_{i+1}^\dagger c_i + {\rm h.c.}\right) \\
&+  \sum_{i}\left( \Delta c_{i} c_{i+1} + {\rm h.c.}\right).
\end{align*}
Using the spinor $\phi_i^\dagger = (c_i^\dagger, c_i)$, we can rewrite the Hamiltonian as
\begin{align*}
&H = \frac{1}{2}\sum_i \phi^\dagger_i H_{BdG,ij} \phi_j,\\
&H_{BdG,ij} = -\mu \tau_z \delta_{ij} - (t \tau_z + i\Delta \tau_y )\delta_{i,j+1}- (t \tau_z - i\Delta \tau_y)\delta_{i,j-1}.
\end{align*}
Note that by taking $t' = \kappa = \kappa = 0$ in the BDI model, Eq. \ref{bdi_model}, we obtain
\begin{align*}
H_{ij} =& m \sigma_x\delta_{ij} + \frac{1}{2} t \left[(\sigma_x + i \sigma_y)\delta_{i,j+1} + (\sigma_x - i \sigma_y) \delta_{i,j-1} \right],
\end{align*}
which is just the Bogoliubov-de Gennes Hamiltonian of the Kitaev chain by rotating $x$ into $z$ and identifying $\mu = -m, t_{\rm Kit} = -t_{BDI}/2, \Delta = -t_{BDI}/2 $. From Fig.\ref{bdi_phase_diagram} we see that the $BDI$ model transitions from $\nu = 1$ to the trivial phase at $t=0, m=\pm t_{BDI}$, or alternatively, when $\mu = \pm 2 t_{Kit}$, which is the known result for the Kitaev chain. Therefore the results already shown for the BDI model studied here are also applicable to the Kitaev chain.

\section{Notes}

So far we show examples of two-band models, where the Zak phase is obtained from the lower occupied band. If we consider systems with a higher number of bands each band carries a Zak phase. We find that if we substitute the projector onto the occupied states, $C$, by a projector to any band $\alpha$ (or set of states), $P_\alpha$, the relations discussed above still hold.

There is one thing one has to be careful about. The Zak phase seems not well-defined for two-band models at gapless points, or at least for finite systems. This seems to generalize to wether or not there is a gap between the set of states chosen to calculate the Zak phase over and the rest.

We encounter another issue. When an inhomogeneous system presents interphases between two different topological phases, and therefore zero-modes, the localization of the entanglement eigenstates does not work as discussed above anymore. The Wannier states are no longer always good approximations in the bulk and we do not have a way of defining a consistent clasification of the bulk states. However, for the cases where $\chi_s$'s width is lower than 1 this classification is not needed and the can still compute the Zak phase.
